---
name: Aymeric
surname: Oliveira-Xavier
position: "PhD Candidate"
#profilepic: "img/aymeric.jpeg"
address: "Université de Sherbrooke, Canada"
phone: +33 652347282
#www: mariecurie.com
email: "oliveira.xavier.aymeric@gmail.com"
#twitter: mariecurie
#github: mariecurie
#linkedin: mariecurie
#aboutme: "insert information about me here"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)

# install.packages("readxl") uncomment this if you need to install the package
library(readxl)
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  # save sheet name for each sheet (list)
  names(list) <- all
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}

filename <- "CV_database.xlsx"
readExcelSheets(filename)
```

# Education

```{r}
education %>% 
  detailed_entries(with,
                   when,
                   what,
                   where,
                   why)
```

# Experience

```{r}
experience %>% 
  detailed_entries(with,
                   when,
                   what,
                   where,
                   why)
```

# Training

```{r}
training %>% 
  detailed_entries(with,
                   when,
                   what,
                   where,
                   why)
```


# Skills

-  **Data analysis & programming** R | RMarkdown | LaTeX | ShinyApp | Figma

-  **Languages** French (Native) | English (Professional) | Spanish (Professional)

-  **Bioacoustic analysis** Kaleidoscope Pro | Audition

-  **Geospatial analysis** QGIS | Fragstats 

-  **Other softwares** Office suite | Photoshop | Premiere Pro

# Extracurriculum activity

```{r}
extracurriculum_activity %>% 
  detailed_entries(with,
                   when,
                   what,
                   where,
                   why)
```

# Grants & fundings

```{r}
grants_and_funding %>% 
  detailed_entries(with,
                   where,
                   what,
                   when,
                   why)
```

# Honors & awards

```{r}
honors_and_awards %>% 
  detailed_entries(with,
                   where,
                   what,
                   when,
                   why)
```

# Publications

```{r}
library(dplyr)
bibliography_entries("papers.bib")
```
